Ecological Modeling HW8

### 2018-05-11 1062_class/eco_model/HW/C8/HW8.Rmd
up

---
title: "Ecological Modeling HW8"
author: Yongfu Liao
date: "`r Sys.Date()`"
output: 
    html_document:
        code_folding: hide
css: ~/local_depend/style_sheets/style.css
---

>>>>

---
title: "Ecological Modeling HW8"
author: Yongfu Liao
date: "`r Sys.Date()`"
output: 
    html_document:
        code_folding: hide
css: /home/liao/local_depend/style_sheets/style.css
---
